### 2019-09-23 reports/thesis/book.tex

In the ABS test sample, voids in the order of millimetres were detectable using this method. However, for the titanium test sample, the voids were undetectable due to dominating edge effects. The reason for this is unknown. It was speculated that the main source of error was from the simulated projection not being quite pixel-perfect aligned causing model misspecification at the edges. Therefore, the method was unable to distinguish disagreement due to model misspecification or a void. This method could be improved if \emph{aRTist} was integrated into it. For example, the simulated projection could be realigned to minimise the number of positives. This will help eliminate sources of error due to \emph{aRTist}. A problem with this suggestion is that aligning the simulated projection is a high dimensional problem \citep{brierley2018optimized}.

Two angular projections were looked at in this thesis. The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection. Defect detection can be tough if a difficult projection angle was used. Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle.

The inference could be improved if the location of the defects were known in the projection. This would allow identifying which positives are true and false positives so that the analysis can be quantified using a ROC curve.

>>>>

Two angular projections were looked at in this thesis. The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection. Defect detection can be tough if a difficult projection angle was used. Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle. Another possible extension is to integrate \emph{aRTist} into the inference. for example, the simulated projection could be realigned to minimise the number of positives. This will help eliminate sources of error due to \emph{aRTist}. A problem with this suggestion is that aligning the simulated projection is a high dimensional problem \citep{brierley2018optimized}.

In the ABS test sample, voids in the order of millimetres were detectable using this method. Further work could include test samples made from materials such as titanium alloys (Ti-6Al-4V). This can be challenging because artefacts, such as streaks, can appear when using XCT for metal parts \citep{deman1998metal, nawaz2014metal}. Another problem is that because titanium products are created using a power-based method, powder may become trapped \citep{brierley2018optimized} in designed voids. This results in voids appearing with less contrast in the projections, making it harder to detect.
